Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-06-19 FIE2019-final-TPJHDsaved.tex
Push on references

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). A multitude of national and international model curricula and recommendations - from national academies, learned societies and even governments -- have been presented and discussed in recent years, with varying levels of impact on policy and practice. In this paper we attempt to address the key questions ``what should the generalist computer scientist/engineer know'' and ``how well is that being taught''. (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters-level discipline; or left for development in professional practice, sometimes called ``information assurance'' in the UK and Europe, which worked, even if not well, in a sequential process model.

Evaluating how cybersecurity is taught in all aspects of computer science is a  task of considerable size. We feel that to do this completely is beyond the scope of our current research and the scope of this paper. We have instead adopted a case study based research approach to evaluate the evidence of the teaching of cybersecurity within general computer science to undergraduate students. Thus, in the context of widespread international computer science/engineering curriculum reform - both in compulsory, as well as post-compulsory education - what does this need to embed cybersecurity mean more generally for institutions and educators, and how do we teach this curricula area?

In this paper, we frame a key social, cultural and economic global challenge of cybersecurity in computing and engineering education by analysing the UK's national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities (and into industry and professional practice). Through this analysis of UK educational policy and practice, we make a number of recommendations for future cybersecurity educational initiatives and interventions, including a number of innovative practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions internationally.
\end{abstract}

@@

\subsection{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The person in the street --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general Computer Science graduate.
\item The general Computer Science masters graduate.
\item The specialist Computer Science graduate.
\item The specialist Computer Science masters graduate.
\end{enumerate}
The focus of this paper is on 2--3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What should be taught to the generalist, and how?
\item[RQ2]Should this be taught stand-alone or integrated? 
\item[RQ3]Can accreditation enhance the provision of cybersecurity within an accrediting bodies jurisdiction?
\end{description}
The ACM/Institute of Electrical and Electronics Engineers (IEEE)-CS Joint Task Force on Computing Curricula,\cite[p.~97]{ACM2013a} takes a distinct view on RQ2:
\begin{quote}
The Information Assurance and Security KA is unique among the set of KAs presented here
given the manner in which the topics are pervasive throughout other Knowledge Areas.
\end{quote}
It proposes 9 ``core'' hours and 63.5 distributed across the other Knowledge Areas.
%\pagebreak - to fix URL issues
\par
Nevertheless, the situation on the ground is different: \cite{Ackerman2019a}, describing the USA, writes as follows
\begin{quote}
Universities suffer shortcomings, as well. Roughly 85 of them offer undergraduate and/or graduate degrees in cybersecurity. There is a big catch, however. Far more diversified computer science programs, which attract substantially more students, don't mandate even one cybersecurity course.
\end{quote}

But \cite[Table 1]{Ruiz2019a} shows that the UK situation is distinctly different: he quotes that 61\% of UK courses offer mandatory cybersecurity content, and his research was based on web scraping, it represents a lower bound.

It is at least plausible to attribute this difference to differences in the accreditation regimes.
\begin{description}
\item[UK]The BCS, The Chartered Institute for IT (BCS) has had a requirement to include information security in the curriculum since 2010, and has expected coverage of an agreed cybersecurity syllabus since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle). More precisely since 2010, accredited degrees have been expected to demonstrate coverage of ``2.1.9 Knowledge and understanding of information security issues in relation to the design, development and the use of information  systems'' \cite[p.~30]{BCS2018a} since 2010 with an enhanced cybersecurity related definition of what this entails since 2015 \cite[p.~17--18]{BCS2018a}.
%BCS has had cybersecurity in the curriculum since 2013, and required cybersecurity in accreditation since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle).
\item[US]ACM has equally had cybersecurity (``Information Assurance and Security'' --- IAS) in the curriculum since 2013 \cite{ACM2013a}, but it is not the accrediting body. ABET is, and is requiring IAS with effect from the 2019-20 cycle (self study reports due 1 July 2019): more precisely \cite[Table 3]{Oudshoornetal2018a} ``The computing topics must include: \dots{} Principles and practices for secure computing \dots. This should mean that  all accredited universities should be compliant by 2025 (because of the six-year cycle).
%\cite[chapter 7]{Davenportminor2019a}.  % need a better reference
\end{description}
\section{Policy Context}

@@

The UK's official knowledge resource, the CyBOK project \cite{Bristol2019a}, has produced reference documentation for some (2 final, 3 for comment out of a planned total of 19) knowledge areas, which are useful references for the experienced educator looking for a definition or characterisation, but a long way from being a textbook (which is not their aim).

Is teaching cybersecurity different? Lecturing is probably not the best way. Should we use real-life case studies (e.g. British Airways \cite{Barth2018a}).  % JHD - need's fixing.

%AI noted the workshops with ISC$^2$, with the ``this is a fad'' concept.  {\bf AI to write up}.
  This raises pedagogic questions which are beyond the scope of this research to resolve. Should we be teaching content because it's underpinning?; or because there's a skill shortage?

>>>>

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). A multitude of national and international model curricula and recommendations 
%-- from national academies, learned societies and even governments -- 
have been presented and discussed in recent years, with varying levels of impact on policy and practice. In this paper we attempt to address the key questions ``what should the generalist computer scientist/engineer know'' and ``how well is that being taught''. (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters-level discipline; or left for development in professional practice, sometimes called ``information assurance'' in the UK and Europe, which worked, even if not well, in a sequential process model.

Evaluating how cybersecurity is taught in all aspects of computer science is a  task of considerable size. We feel that to do this completely is beyond the scope of our current research and the scope of this paper. We have instead adopted a case study based research approach to evaluate the evidence of the teaching of cybersecurity within general computer science to undergraduate students. Thus, in the context of widespread international computer science/engineering curriculum reform, %- both in compulsory, as well as post-compulsory education - 
what does this need to embed cybersecurity mean more generally for institutions and educators, and how do we teach this subject?

In this paper, we frame a key social, cultural and economic global challenge of cybersecurity in computing and engineering education by dThrough this analysis of UK educational policy and practice, we make a number of recommendations for future cybersecurity educational initiatives and interventions, including a number of innovative practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions internationally.
\end{abstract}

@@

\subsection{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The person in the street --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general Computer Science graduate.
\item The general Computer Science masters graduate.
\item The specialist Computer Science graduate.
\item The specialist Computer Science masters graduate.
\end{enumerate}
The focus of this paper is on 2--3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What should be taught to the generalist, and how?
\item[RQ2]Should this be taught stand-alone or integrated? 
\item[RQ3]Can accreditation enhance the provision of cybersecurity within an accrediting bodies jurisdiction?
\end{description}
The ACM/Institute of Electrical and Electronics Engineers (IEEE)-CS Joint Task Force on Computing Curricula,\cite[p.~97]{ACM2013a} takes a distinct view on RQ2:
\begin{quote}
The Information Assurance and Security Knowledge Area (KA) is unique among the set of KAs presented here
given the manner in which the topics are pervasive throughout other KAs.
\end{quote}
It proposes 9 ``core'' hours and 63.5 distributed across the other Knowledge Areas.
%\pagebreak - to fix URL issues
\par
Nevertheless, the situation on the ground is different: \cite{Ackerman2019a}, describing the USA, writes as follows
\begin{quote}
Universities suffer shortcomings, as well. Roughly 85 of them offer undergraduate and/or graduate degrees in cybersecurity. There is a big catch, however. Far more diversified computer science programs, which attract substantially more students, don't mandate even one cybersecurity course.
\end{quote}

But \cite[Table 1]{Ruiz2019a} shows that the UK situation is distinctly different: he quotes that 61\% of UK courses offer mandatory cybersecurity content, and, as his research was based on web scraping, this represents a lower bound.

It is at least plausible to attribute this difference to differences in the accreditation regimes.
\begin{description}
\item[UK]The BCS, The Chartered Institute for IT (BCS) has had a requirement to include information security in the curriculum since 2010, and has expected coverage of an agreed cybersecurity syllabus since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle). More precisely since 2010, accredited degrees have been expected to demonstrate coverage of ``2.1.9 Knowledge and understanding of information security issues in relation to the design, development and the use of information  systems'' \cite[p.~30]{BCS2018a} %since 2010 redundant
	with an enhanced cybersecurity related definition of what this entails since 2015 \cite[p.~17--18]{BCS2018a}.
%BCS has had cybersecurity in the curriculum since 2013, and required cybersecurity in accreditation since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle).
\item[US]ACM has equally had cybersecurity (``Information Assurance and Security'' --- IAS) in the curriculum since 2013 \cite{ACM2013a}, but it is not the accrediting body. ABET is, and is requiring IAS with effect from the 2019-20 cycle (self study reports due 1 July 2019): more precisely \cite[Table 3]{Oudshoornetal2018a} ``The computing topics must include: \dots{} Principles and practices for secure computing \dots.'' This should mean that  all accredited universities should be compliant by 2025 (because of the six-year cycle).
%\cite[chapter 7]{Davenportminor2019a}.  % need a better reference
\end{description}
\section{Policy Context}

@@

The UK's official knowledge resource, the CyBOK project \cite{Bristol2019a}, has produced reference documentation for some
%JHD:  was 2/3, now 5/7
 (5 final, 7 for comment out of a planned total of 19) knowledge areas, which are useful references for the experienced educator looking for a definition or characterisation, but a long way from being a textbook (which is not their aim).

Is teaching cybersecurity different? Lecturing is probably not the best way. Should we use real-life case studies (e.g. British Airways \cite{Barth2018a}). \cite{Weiss:2013:THC:2527148.2527180} suggests that there are benefits from teaching this discipline area in a more practical manner.

%AI noted the workshops with ISC$^2$, with the ``this is a fad'' concept.  {\bf AI to write up}.
  % Should we remove this?  This raises pedagogic questions which are beyond the scope of this research to resolve. Should we be teaching content because it's underpinning?; or because there's a skill shortage?
